---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

[![stability-experimental](https://img.shields.io/badge/stability-experimental-orange.svg)](https://github.com/joethorley/stability-badges#experimental)
[![Travis-CI Build Status](https://travis-ci.org/poissonconsulting/poissqlite.svg?branch=master)](https://travis-ci.org/poissonconsulting/poissqlite)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/poissonconsulting/poissqlite?branch=master&svg=true)](https://ci.appveyor.com/project/poissonconsulting/poissqlite)
[![Coverage Status](https://img.shields.io/codecov/c/github/poissonconsulting/poissqlite/master.svg)](https://codecov.io/github/poissonconsulting/poissqlite?branch=master)
[![License: MIT](https://img.shields.io/badge/License-MIT-blue.svg)](https://opensource.org/licenses/MIT)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/poissqlite)](https://cran.r-project.org/package=poissqlite)

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# poissqlite

An R package to facilitate working with SQLite databases.

## Documentation

### BLOBs

Files can be added to SQLite databases as storage type [BLOB](https://sqlite.org/datatype3.html).

The `ps_blob_file()` function can be used to convert a file to a blob (R object of class raw) while `ps_deblob_file()` performs the inverse operation, i.e., saves a blob to a file of the original format. `ps_blob_files()` and  `ps_deblob_files()` are the equivalent functions for working with multiple files.
In addition, the `ps_blob_object()` and `ps_deblob_object()` can be used to convert between an R object and a blob. This is achieved by reading or writing the object as an `.rds` file which means that `ps_deblob_file()` applied to a blob created using `ps_blob_object()` saves the intermediate `.rds` file.

It's important to realize that the `ps_blob` family of functions embed the original file extension in the raw data to ensure the converted files are the original format. A consequence of this is that when deblobbing, file names should not include an extension (file extensions can be removed using `tools::file_path_sans_ext()`). A second consequence is that the `ps_deblob` family of functions will only work on blobs created using `ps_blob`.


```{r blob}
library(poissqlite)
mat <- matrix(1:9, nrow = 3)
blob <- ps_blob_object(mat)
print(blob)
ps_deblob_object(blob)
```

## Installation

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("poissonconsulting/poissqlite")
```

## Contribution

Please report any [issues](https://github.com/poissonconsulting/poissqlite/issues).

[Pull requests](https://github.com/poissonconsulting/poissqlite/pulls) are always welcome.

Please note that this project is released with a [Contributor Code of Conduct](https://github.com/poissonconsulting/poissqlite/CONDUCT.md). 
By participating in this project you agree to abide by its terms.
